LogChunks: A Data Set for Build Log Analysis

### 2019-12-19 msr-paper/paper.tex
bit more shortening to get under 4 pages :)

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
	\caption{Overview of \emph{LogChunks}}
	\label{fig:lc-overview}
\end{figure}

@@

This section describes the file structure and the data schema of \emph{LogChunks}.
We give a detailed explanation for the manually labeled data.

\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
Each contains folders representing the main languages of the repositories in \emph{LogChunks}.

The logs are organized in folders for each repository, identified by \texttt{\textless repository\_owner\textgreater @\textless repository\_name\textgreater }.
Within each repository folder the logs are separated according to build status.
%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
The build status folder contains the full logs in files named with the ID of the build that produced the log.

@@

\lstset{
  language=XML,
  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
	frame=single,
	escapeinside=**
}
\begin{figure}[]
	\centering
\begin{lstlisting}[breaklines=true]
<Examples>
  <Log>C/php@php-src/failed/529279089.log</Log>
    <Keywords>ERROR, FAIL, DIFF</Keywords>
    <Category>0</Category>
    <Chunk>001+ ** ERROR: process timed out **
001- OK.
========DONE========
FAIL Bug #60120 (proc_open hangs when data in stdin/out/err is getting larger or equal to 2048)</Chunk>
  </Example>
  ...
</Examples>
\end{lstlisting}
	\caption{Example XML file from \emph{LogChunks}}
	\label{lst:examples}
\end{figure}

@@

@@

\paragraph{Keywords}
We presented the \texttt{Chunk} and ten lines above and below to the labeler.
Their task was to note down three strings they would put into a search field to find this failure description.
The strings should appear in or around the \texttt{Chunk} and is case-sensitive.
There are no special limitations on the string itself, especially spaces are allowed.

\paragraph{Category}
To label the \emph{structural categories} we presented the \texttt{Chunk} and the surrounding context to the labeler for all logs from a repository.
We asked them to assign numerical categories according to whether the \texttt{Chunk} had the same structural representation.
The labeler should start the categories with 0 and increase as new ones appear.
%For reproducibility, we presented the logs in chronological build order.

@@

\paragraph{Results}
In total we sent out mails to 246 developers, asking about 3.2 build logs per mail on average.
32 of these mails could not be delivered, e.g.\ because they were addressed to \emph{noreply} mail addresses.
%These 32 mails related to 68 of the build logs.
We received answers from 61 developers, corresponding with 144 build logs.
%Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails and logs answered about, not delivered and unanswered.

>>>>

\begin{figure}[tbp]
	\centering
	\includegraphics[width=\columnwidth, trim={2cm 2cm 2cm 0.5cm}, clip]{overview.pdf}
	\caption{Overview of \emph{LogChunks}}
	\label{fig:lc-overview}
\end{figure}

@@

This section presents the file structure and the data schema of \emph{LogChunks}.
%We give a description of the manually labeled data.
%\emph{LogChunks} has two top level folders, \texttt{build-failure-reason} and \texttt{logs}.
%Each contains folders representing the main languages of the repositories in \emph{LogChunks}.
The build logs are organized in folders for each language and repository.
Within each repository folder, folders for each build status contain the log files named with the corresponding build ID.
% the logs are separated according to build status.
%Currently, \emph{LogChunks} only contains logs from \texttt{failed} builds.
%The build status folder contains the full logs in files named with the ID of the build that produced the log.

@@

@@

\lstset{
  language=XML,
  morekeywords={Examples, Example, Log, Keywords, Category, Chunk},
  postbreak=\mbox{\textcolor{cyan}{$\hookrightarrow$}\space},
	frame=single,
	escapeinside=**
}
\begin{figure}[]
	\centering
\begin{lstlisting}[breaklines=true]
<Examples>
  <Log>C/php@php-src/failed/529279089.log</Log>
    <Keywords>ERROR, FAIL, DIFF</Keywords>
    <Category>0</Category>
    <Chunk>001+ ** ERROR: process timed out **
001- OK.
========DONE========
FAIL Bug #60120 (proc_open hangs)</Chunk>
  </Example>
  ...
</Examples>
\end{lstlisting}
	\caption{Example XML file from \emph{LogChunks}}
	\label{lst:examples}
\end{figure}

@@

\paragraph{Keywords}
We presented the \texttt{Chunk} and ten lines above and below to the labeler.
Their task was to note down three strings they would put into a search field to find this failure description.
The strings should appear in or around the \texttt{Chunk} and is case-sensitive.
There are no limitations on the search string, especially spaces are allowed.

\paragraph{Category}
To label the \emph{structural categories} we presented the \texttt{Chunk} and the surrounding context to the labeler for all logs from a repository.
We asked them to assign numerical categories according to whether the \texttt{Chunk} had the same structural representation.
%The labeler should start the categories with 0 and increase as new ones appear.
%For reproducibility, we presented the logs in chronological build order.

@@

\paragraph{Results}
In total we sent out mails to 246 developers.%, asking about 3.2 build logs per mail on average.
32 of these mails could not be delivered, e.g.\ because they were addressed to \emph{noreply} addresses.
%These 32 mails related to 68 of the build logs.
We received answers from 61 developers, corresponding with 144 build logs.
%Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig:mails-answers-received-builds} show the proportions of mails and logs answered about, not delivered and unanswered.
